### 2021-12-22 README.Rmd
MORE README ENHANCEMENTS & EDITS

This repository contains the research compendium in support of the above titled paper.
The manuscript is currently in preparation and the text, code, analysis, and results
are under active development.

>>>>

This repository serves as the research compendium in support of the above titled paper.
As the manuscript works its way through peer review and the publications process,
additional reproducibility features (e.g. Dockerfile, MyBinder.org) and
an R/Shiny application to explore results will be made available.

Major releases of the research compendium are published and archived with Zenodo [https://doi.org/10.5281/zenodo.4638221](https://doi.org/10.5281/zenodo.4638221)
